Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2017-05-19 response_letter/response_letter.tex

%% LyX 2.1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
%\RequirePackage[loading]{tracefnt}
\documentclass[10pt,a4paper,titlepage,conference]{article}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel} 
\usepackage{units}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\special{papersize=\the\paperwidth,\the\paperheight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[8pt,titlepage,a4paper]{article}%{/usr/share/texmf-dist/tex/latex/IEEEtran/IEEEtran}
%\documentclass[11pt,titlepage,a4paper]{/usr/share/texmf-dist/tex/latex/IEEEtran/IEEEtran}
%\usepackage[latin2]{inputenc}
%\usepackage{times}
%\renewcommand\baselinestretch{1.5}  % 
\usepackage{color}
\usepackage{wrapfig}
\usepackage{epsfig}
%\usepackage{CoverPage}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{holtpolt}
\usepackage{turnstile}
\usepackage{tikz}
\usepackage{bm}
\usepackage{cite}
\usepackage[multiple]{footmisc}
%\usepackage{calrsfs}
\usetikzlibrary[arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri]

\def\bo#1{{\bf{#1}}}
\def\E{{\rm{E}}}
\def\grebo#1{\mbox{\boldmath$#1$}}
\def\bold#1{\mbox{\boldmath$#1$}}
\def\conv{*}

\def\date#1{\def\@date{#1}}
\def\version#1{\def\@version{#1}}
\def\author#1{\def\@author{#1}}
\def\title#1{\def\@title{#1}}
\def\assignment#1{\def\@assignment{{\it #1}}}
\newcommand{\var}{\rm{var}}

\newcommand{\unfootnote}[1]{
  \renewcommand{\@makefnmark}{}
  \footnotetext{#1}
  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
}

% \papertitle[title of the paper][Author(s)][Conference type][date + place] 
%\graphicspath{{fig/}}

\begin{document}

\section{Common Questions and Corresponding Answers}
\begin{itemize}
  \item CQ1: \emph{Lacking novelty compared to ICC}
  \item A1: Quoting the part of the cover letter for IEEE transaction submission:\newline
  \sc{Compared with the conference version, the major contributions and differences of this submitted manuscript are summarized as follows:
  \begin{enumerate} 
  \item We introduce additional performance analysis results for constellations in an uncoded system and an in-depth discussion of the observed results.
  \item We extend the section dealing with the adaptive constellation design in an uncoded system and we supplement additional HW evaluation results for the adaptive system in the whole range of observed channel SNRs. Again a close agreement between between the analytic and measurement results is shown.
  \item We show how the channel coding can be integrated into the proposed constellation design, including the cut-set bound analysis of proper source transmission rates, which provides a hint for the setup of all channel encoders' rates in the system.
  \item We evaluate numerically the performance of the resulting adaptive modulation-coding scheme
  for a wide range of channel conditions in the WBN and we emphasise the performance gains with
    respect to the uncoded system.
  \item We perform a simple robustness analysis, demonstrating that the proposed modulation and coding strategy is viable even in the case when the real world condition induce some deviations from the mathematical system model assumed in the paper.
  \end{enumerate}
  }
  I believe that this answer could be enough. (Actualization -TODO)
\end{itemize}

\begin{itemize}
  \item CQ2: \emph{Better reference scenario?}
  \item A2: Related with two-step vs 3(4) step comparison requiring additional derivations (TODO)
\end{itemize}

\begin{itemize}
  \item CQ2: \emph{Typos and Formating Issues?}
  \item A3: We have proofreaded the manuscript for typos. Regarding the formating issues, we prefer
  to clean final version of the manuscript. (TODO)
\end{itemize}

\subsubsection*{Reviewer 1}
\begin{itemize}
  \item Q: \emph{The weak aspect of this paper is that the current paper is a small variation of a
  previous paper by the authors. The authors should further highlight the difference of this paper.}
  \item A: See A1
\end{itemize}

\begin{itemize}
  \item \emph{The authors should edit the paper more carefully. For example, in Figure 5, the
  references are missing. Please go over the whole the paper and make sure similar issues do not
  exist}
  \item A: See A3
\end{itemize}

\subsubsection*{Reviewer 2}
\begin{itemize}
  \item Q: \emph{Since this work builds upon previous work on the application of wireless network
  coding to the WBN, novelty is slightly lacking}
  \item A: see A1
\end{itemize}

\begin{itemize}
  \item Q: \emph{The proposed scheme appears to be quite specific to the WBN, I wonder if it is
  possible to generalize to other similar networks where linear codes yield a good performance.}
  \item A: We should stress that the modulation design covers both
  wireless network coding and processing the signal from multiple stages. Join generalization of
  both phenomenons in the way we did would be extremely challenging, because of synchronization,
  pre-rotation, etc. Also note that our approach is basically a practical instance of a well known
  theoretical principle with application of WNC to approximately equal power levels and
  interference cancellation on significantly different power levels. So that its generalization in
  theoretical level is already known. This answers also general comments.
\end{itemize}

\begin{itemize}
  \item Q: \emph{The authors should also provide more insight or intuition on the design of the
  constellation and explain why the challenges to apply to other linear networks.}
  \item A: The intuition beyond the design could be partly found in ICC (TODO)
\end{itemize}

\begin{itemize}
  \item Q: \emph{-It might be useful to the reader to add a figure for the butterfly network in the
  setting of algebraic network coding for comparison.}
  \item A: see A2
\end{itemize}

\subsubsection*{Reviewer 3}
\begin{itemize}
  \item Q: \emph{In figure 6, 7, 8, 9, the reference scheme using QPSK always has a zero throughput,
  which demonstrates that this reference modulation scheme does not work at all in WBN under the
  proposed SNRs. Then the proposed communication scheme is claimed to have performance enhancement
  for sure. However, logically, this only demonstrates that the proposed algorithm gives positive
    throughput in WBN instead of not working. But it is not enough to say it gives a "performance
    enhancement" comparing with a previous working scheme. So it would be better if the author can
    further compare some other modulation schemes which can also give some positive throughput in
    WBN.}
  \item A: partly see A2 for join decoding. Partly I remove throughput gain for (1,1) strategy
  compared to QPSK (TODO) 
\end{itemize}

\begin{itemize}
  \item Q: \emph{As far as we know, according to the 3GPP protocol, there is a Channel Quality Index
  (CQI) vs. modulation format table, which suggests the modulation scheme with respect to difference
  SNR range. According to this table, for example, for the SNR varying from 6dB to 20dB, the
  protocol suggests using 16QAM and 64QAM instead of QPSK. In WBN, it could be different from 3GPP,
  but I suggest the author to test some other reference modulation format and compare the
  difference. }
  \item A: The channel quality index is 3-dimensional (MAC, BC and HSI) in our case and we
    have it basically presented in the manuscript in form some cuts shown in figures. Its comparison
    with P2P case can be conducted in multiple ways (e.g. one can consider 4-step conventional P2P),
    but we solve again the problem two-step versus 4-step stage (see A2).
\end{itemize}

\begin{itemize}
  \item Q: \emph{Although, in the future work, the authors have mentioned the fading channel case, it would still be better that the case of fading channels or of longer communication distance could be simulated and experimented. AWGN channel seems to be too ideal. If some initial results on the fading channel case can be added into the paper, it would be better.}
  \item A: TODO (possible to play with in the tutorial)
\end{itemize}

\begin{itemize}
  \item Q: \emph{The robustness analysis is important, and the authors have done some simulations on this aspect. However, it would be more appreciated if a hardware experiment can be done on this aspect.}
  \item A: It actually is - check Figure 17
\end{itemize}

\begin{itemize}
  \item Q: \emph{In Fig. 15, the throughput enhancmence for the coding scheme is shown. It is
  interesting to see that the throughput enhancment has some "peak" and "valley" as the γ\_MAC
  increases. If possible, please give some explanation. Or this is just a random instance that
  happens to be shown by the hardware experiment, that is also fine.}
  \item A: The explanation here is quite straightforward, as it follows from the steep
  gradients of the uncoded throughput as function of SNRs shown in Figure 10. On the other hand the
  coded throughput as a function of SNRs is much smoother (Figure 14) and therefore their difference
  induces peeks and valleys
\end{itemize}

\begin{itemize}
  \item Q: \emph{There are also some minor context error or typos found}
  \item A: See A3
\end{itemize}

\section{Major Changes Summary}
\begin{itemize}
\item
\end{itemize}

\end{document}

### 2017-05-19 Const_design_final.tex
Added gitignore, figures, template and bibfile

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\includegraphics[width=0.8\textwidth]{fig/d2_1}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/const_all_2}
\par\end{centering}

@@

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.
\begin{figure}
\centering{}
\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}
\caption{Setup for HW evaluation (Ettus Research
USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
to imitate the AWGN channel conditions (as used in the numerical evaluation).
To allow a strict control of HSI channels SNR in the HW
setup, the HSI channels are emulated by adding a Gaussian noise to
the respective source signal and the resulting emulated HSI is passed
to destinations via UDP. This also avoids the problem of node visibility
where direct links $S_{A}\rightarrow D_{A}$ and $S_{B}\rightarrow D_{B}$
exist in the laboratory environment.\label{fig:CTUpp_HW_setup}}
\end{figure}

@@

\begin{itemize}
\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
detection at the relay and hence they do not exploit the HSI channels
(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
these constellations significantly outperform those with $N_{b}=0$
or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
and consequently in a more reliable overheard HSI for the constellations
with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
symbol transmitted by the sources.
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=16\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput16_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=17\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=17\,\mathrm{dB}$
and given $(N_{b},N_{s})$.\label{fig:CTUpp_Throughput17_17}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
\par\end{centering}

@@

After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
destination nodes.
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
\par\end{centering}

>>>>

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{figure*}
\begin{centering}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\par\end{centering}

@@

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.
\begin{figure}
\centering{}
\caption{Setup for HW evaluation (Ettus Research
USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
to imitate the AWGN channel conditions (as used in the numerical evaluation).
To allow a strict control of HSI channels SNR in the HW
setup, the HSI channels are emulated by adding a Gaussian noise to
the respective source signal and the resulting emulated HSI is passed
to destinations via UDP. This also avoids the problem of node visibility
where direct links $S_{A}\rightarrow D_{A}$ and $S_{B}\rightarrow D_{B}$
exist in the laboratory environment.\label{fig:CTUpp_HW_setup}}
\end{figure}

@@

\begin{itemize}
\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
detection at the relay and hence they do not exploit the HSI channels
(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
these constellations significantly outperform those with $N_{b}=0$
or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
and consequently in a more reliable overheard HSI for the constellations
with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
symbol transmitted by the sources.
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=16\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput16_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=17\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=17\,\mathrm{dB}$
and given $(N_{b},N_{s})$.\label{fig:CTUpp_Throughput17_17}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\par\end{centering}

@@

After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
destination nodes.
\begin{figure*}
\begin{centering}
\par\end{centering}
